% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008-2014 Nathaniel Johnston <nathaniel@njohnston.ca> http://www.njohnston.ca
% (c) 2017-2021 Alexandre Pinto <alexandpinto@gmail.com> http://www.alexpnt.github.io
%
% Depending on your TeX distribution, you may need to download the revnum and longtable packages for this template to work!
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[usenames,dvipsnames,letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage{array}
\usepackage[svgnames]{xcolor}
\usepackage{enumerate}
\usepackage{framed}
\usepackage{longtable}
\usepackage{revnum}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{tocloft}
\usepackage[textwidth=18cm,textheight=25cm]{geometry} % Edit as required
\usepackage[utf8]{inputenc}
\usepackage{marvosym}
\usepackage[document]{ragged2e}
\usepackage{multicol}


%\usepackage[defaultsans]{droidsans}
%\usepackage[default]{comfortaa}
\usepackage{cmbright}
%\usepackage[default]{raleway}
%\usepackage{fetamont}
%\usepackage[default]{gillius}
%\usepackage[light,math]{iwona} 

% set font default
\renewcommand*\familydefault{\sfdefault} 	
\usepackage[T1]{fontenc}
\usepackage{fontawesome}

\include{cv-custom} 
%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{1}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{1}  % Inner background color of title bars
\definecolor{babyblue}{RGB}{0,150,255}


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}
\setlength\LTleft{0.2in} % needed to make longtable full-width
\setlength\LTright{0.2in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\comment}[1]{}
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\fboxsep}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}

\newcommand{\colorhref}[3][babyblue]{\href{#2}{\color{#1}{#3}}}%

% the next four commands allow for the \ressubheading environment to be 1, 2, 3, or 4 subrows, depending on which command you use. This is admittedly hack-ish, and should probably be replaced by a single more flexible command (with optional arguments) in the future
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}[t]{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
\newcommand{\ressubheadingb}[6]{
\begin{tabular*}{6.5in}[t]{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
		\textit{#5} & \textit{#6} \\
\end{tabular*}\vspace{-6pt}}
\newcommand{\ressubheadingc}[8]{
\begin{tabular*}{6.5in}[t]{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
		\textit{#5} & \textit{#6} \\
		\textit{#7} & \textit{#8} \\
\end{tabular*}\vspace{-6pt}}
\newcommand\foo[9]{%
    \def\tempb{#2}%
    \def\tempc{#3}%
    \def\tempd{#4}%
    \def\tempe{#5}%
    \def\tempf{#6}%
    \def\tempg{#7}%
    \def\temph{#8}%
    \def\tempi{#9}%
    \foocontinued
}
\newcommand\foocontinued[7]{%
    % Do whatever you want with your 9+7 arguments here.
}

\newcommand{\ressubheadingd}[1]{
	\def\argten{#1}%
	\ressubheadingdb
}
\newcommand{\ressubheadingdb}[9]{
\begin{tabular*}{6.5in}[t]{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{\argten} & #1 \\
		\textit{#2} & \textit{#3} \\
		\textit{#4} & \textit{#5} \\
		\textit{#6} & \textit{#7} \\
		\textit{#8} & \textit{#9} \\
\end{tabular*}\vspace{-6pt}}


%-----------------------------------------------------------


\begin{document}
{\large \begin{tabular*}{7in}{l@{\extracolsep{\fill}}l} 

\textbf{\LARGE Alexandre Pinto}\smallskip & \smallskip \\
Software/Machine Learning Engineer \\
Coimbra, Portugal& 


\colorhref{alexandpinto@gmail.com}{\small \faEnvelope{} | alexandpinto@gmail.com}\\ 
& \colorhref{https://alexpnt.github.io}{\small \faGlobe{} | alexpnt.github.io}\\
 & \colorhref{https://github.com/alexpnt}{\small \faGithub{} | alexpnt}\\
 &  \colorhref{https://www.linkedin.com/in/alexandre-pinto}{\small \faLinkedin{} | alexandre-pinto}\\

\end{tabular*}}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Software engineer competent in implementing backend systems with focus on machine learning services. \\
Enjoys tackling engineering problems with good system design choices, clarity, scalability and performance.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{ftabular}{p{4cm}|p{12cm}}
\textbf{\small{Nov 2017 - Present}} & \textbf{Machine Learning Engineer -} \textbf{\colorhref{https://www.wit-software.com/}{WIT software}} \\
& At WIT, I am responsible for turning machine learning experiments and proof-of-concept prototypes into production-ready solutions, always having performance and scalability in mind. I work mostly in the Natural Language Processing (NLP) sub-field of Artificial Intelligence, using state-of-art methods. My daily work encompasses all stages of research, design, implementation and testing of machine learning services (\colorhref{https://www.wcp.ai}{https://www.wcp.ai}).\\\\
 & \textit{Technologies: Python, NumPy, Pandas, Scikit-learn, XGBoost, \hfill \break Tensorflow,  Docker, Ansible, Git.} \\


  
\end{ftabular}
\vspace{0.25cm}

\begin{ftabular}{p{4cm}|p{12cm}}
\textbf{\small{Nov 2016 - Oct 2017}} & \textbf{Backend Developer -} \textbf{\colorhref{http://www.ubiwhere.com/en/}{Ubiwhere}} \\
 & At Ubiwhere, I was part of the core team responsible for developing a smart water consumption platform for the city of Porto, Portugal. This meant building a system with high-availability, multi-tenancy and concurrency support. My job consisted in implementing REST APIs and developing the core of the backend web services. Furthermore, I was also involved in the development of the frontend mobile app, used by hundreds of users and available in multiple mobile operating systems such as Android and iOS (\colorhref{https://www.ubiwhere.com/en/case-studies/smart-cities/app-aguas-do-porto}{app-aguas-do-porto}).  \\\\
 & \textit{Technologies: Django/Python, Django REST Framework, Ionic, Docker, Git.} \\
  
\end{ftabular}
\vspace{0.25cm}

\begin{ftabular}{p{4cm}|p{12cm}}
\textbf{\small{Oct 2015 - Jul 2016}} & \textbf{Machine Learning Research Intern -} \textbf{\colorhref{https://www.inesctec.pt/en/centres/cracs}{INESCTEC}} / \textbf{\colorhref{https://www.cisuc.uc.pt/}{CISUC}} \\
 & At INESC TEC/CISUC, I was involved in a research team that developed a filter system (\colorhref{https://www.inesctec.pt/en/news/reminds-project-provides-an-automatic-learning-system-on-relevance-detection}{REMINDS}) that classifies public social data according to their potential relevance to a general audience, filtering out irrelevant information and relying primarily on linguistic and journalistic features.\\\\
 & \textit{Technologies: Python, NumPy, Pandas, Scikit-learn, Matplotlib, Seaborn, PyQt5.}\\
  
\end{ftabular}
\vspace{0.25cm}

\begin{ftabular}{p{4cm}|p{12cm}}
\textbf{\small{Oct 2013 - Mar 2014}} & \textbf{Software Developer -} \textbf{\colorhref{http://ipn.pt/laboratorio/LIS}{Pedro Nunes Institute (IPN)}} \\
 & At IPN (Laboratory for Informatics and Systems), I maintained and developed new features for the information systems.
\\\\
 & \textit{Technologies: Apache Struts/Java, Ruby on Rails/Ruby, Git.}\\

\end{ftabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Relevant Technical Skills}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize*}
\item{\textbf{Programming Languages:} Proficient in Python, C and Java. Able to quickly learn new a language. Very focused on fundamentals that are transferable across different languages.}
\item{\textbf{Programming Paradigms:} Object Oriented, Procedural, Distributed/Concurrent programming, Data-driven/Event programming.}
\item{\textbf{Web Frameworks:} FastAPI, Falcon, Flask, Django, Django Rest Framework.}
\item{\textbf{Web protocols:} REST/RPC, gRPC with protocol buffers. }
\item{\textbf{Machine Learning Tools:} scikit-learn, XGBoost, SciPy stack (NumPy, Matplotlib, pandas), seaborn. Familiar with Keras/Tensorflow.}
\item{\textbf{Artificial Intelligence Theory:} Supervised/Unsupervised Learning Algorithms, Natural Language Processing, Evolutionary Computation.}
\item{\textbf{Data Structures and Algorithms:} Knowledge of different data structures and optimization algorithms.}
\item{\textbf{Control Version Systems:} Git.}
\item{\textbf{CI/CD Systems:} Jenkins.}
\item{\textbf{Relational Databases:} PostgreSQL, MySQL.}
\item{\textbf{NoSQL Databases:} MongoDB.}
\item{\textbf{Deployment Tools:} Ansible, Docker.}
%\item{\textbf{Semantic Web:} Ontologies Representation (RDF,OWL), Triple Stores, SPARQL, Apache Jena, NLTK.}%
%\item{\textbf{Hybrid Mobile App Frameworks:} Ionic.}%
\item{\textbf{Development Tools:} Jetbrains Suite (PyCharm, IntelliJ, Datagrip, WebStorm), Sublime Text Editor, Unix shells.}
\item{\textbf{Cloud Computing:} AWS EC2}
\item{\textbf{Web Frontends:} Proficient with HTML. Familiar with CSS.}
\item{\textbf{Operating Systems:} Competent in GNU/Linux. Familiar with Windows.}
\item{\textbf{Productivity/Project Management Tools:} Trello, Redmine, Slack.}
\item{\textbf{Languages:} Portuguese (fluent, native), English (very good).}
\item{\textbf{Professional Soft Skills:} Self-motivated, Self-learner, Team Player, Planning and Organizational Skills. }
\item{\textbf{Professional ethics:} Follower of industry best practices and strong advocate of rational decisions that minimize long-term negative effects in software development.}
%\item{\textbf{Activities \& Interests:} Programming, Reading, Exercising.}%

\end{itemize*}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education and training}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
	\ressubheading{University of Coimbra}{}{Master Degree in Informatics Engineering - Intelligent Systems}{2013 -- 2016}
	\begin{itemize}
		\resitem{Graduated with 15/20 average}
		\resitem{Dissertation titled “Classification of Social Media Posts according to their Relevance”}
	\end{itemize}
\comment{
	\ressubheading{}{}{Relevant Courses:}{}
	\begin{itemize}
		\resitem{Pattern Recognition, Artificial Intelligence}
		\resitem{Evolutionary Computation, Adaptive Computation}
		\resitem{Semantic Web, Internet Applications}
		\resitem{Project Management, Systems Integration}
		\resitem{Information Theory, Statistics, Technical Communication}
	\end{itemize}
}
\item
	\ressubheading{University of Coimbra}{}{Bachelor Degree in Informatics Engineering}{2010 -- 2013}
	\begin{itemize}
		\resitem{Admission Grade: 17.55/20 }
		\resitem{Graduated with 16/20 average}
	\end{itemize}
\item
	\ressubheading{High School - Quinta das Flores}{}{Science and Technology Course }{2007 -- 2010}
	\begin{itemize}
		\resitem{Graduated with 16/20 average}
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item
	\ressubheading{{\colorhref[black]{https://link.springer.com/article/10.1007\%2Fs00354-017-0015-1}{Predicting the Relevance of Social Media Posts Based on Linguistic Features}}}{}{Alexandre Pinto and Gonçalo Oliveira, H, and Alves, A., New Generation Computing, 2017}{}

	
\item
	\ressubheading{\colorhref[black]{http://drops.dagstuhl.de/opus/volltexte/2016/6008/pdf/OASIcs-SLATE-2016-3.pdf}{Comparing the Performance of Different NLP Toolkits in Formal and Social Media Text}}{}{Alexandre Pinto and Gonçalo Oliveira, H, and Alves, A., pp 1--16, vol 51, SLATE, 2016}{}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Awards, Grants \& Honours}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\vspace{-10pt}
	\begin{center}\begin{longtable}{l@{\extracolsep{\fill}}r}
		\multicolumn{2}{c}{Award to the 3\% Best Students \cftdotfill{\cftdotsep}2010 -- 2011}\\
		\multicolumn{2}{c}{Award to the 3\% Best Students \cftdotfill{\cftdotsep}2011 -- 2012}\\
		\vphantom{E}
\end{longtable}
\end{center}

\clearpage



\iffalse

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Relevant Academic Projects}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\vspace{0.25cm}

\begin{ftabular}{p{4cm}|p{12cm}}
\textsc{\small{Mar 2016 - May 2016}\hspace{1cm}} & \textbf{Default Credit Card Prediction} \\
 & This project was carried out in the context of the Pattern Recognition course. The goal of this project was to develop classifiers to predict if a given client would be able to pay (or not) its credit card in the next month. The project followed the various steps of a typical machine learning pipeline (data preprocessing, feature selection/reduction, classification and evaluation). \\\\
 &  \textit{Technologies: NumPy, Pandas, Scikit-learn, Matplotlib, Seaborn, PyQt5.}\\
 & 
 
\end{ftabular}

\vspace{0.25cm}

\begin{ftabular}{p{4cm}|p{12cm}}
\textsc{\small{Feb 2014 - May 2014}\hspace{1cm}} & \textbf{Predicting the memorability of images} \\
 & This project was carried out in the context of the Artificial Intelligence course. The goal of this project was the automatic classification of images into a degree of memorability by computing their levels of attention according to a set of dimensions.\\\\
 & \textit{Technologies: NumPy, Pandas, Scikit-learn.}\\
 & 
 
\end{ftabular}

\vspace{0.25cm}

\begin{ftabular}{p{4cm}|p{12cm}}
\textsc{\small{Feb 2014 - May 2014}\hspace{1cm}} & \textbf{Semantic Search and
Recommendation in eCommerce} \\
 & This project was carried out in the context of the Semantic Web course. The objective of the project was to build an ecommerce website where users could search for electronic products, browse product categories and get recommendations.\\\\
 & \textit{Technologies: Protégé (Ontology editor), Apache Jena, Apache Tomcat.}\\
 &
 
\end{ftabular}

\vspace{0.25cm}

\begin{ftabular}{p{4cm}|p{12cm}}
\textsc{\small{Feb 2014 - May 2014}\hspace{1cm}} & \textbf{Expert Contact} \\
 & This project was carried out in the context of the Software Project Management course. The objective of the project was to build a new way of communication between the nurses and patients with breast cancer during chemotherapy sessions. This project was a partnership between the research team working at Institute of Health and Care Sciences of the University of Gotemburg and the University of Coimbra and was conducted by a multidisciplinary team.\\\\
 & \textit{Technologies: Apache Struts, Hibernate, HTML, CSS(Bootstrap), Javacript, Git.}\\
 
\end{ftabular}

\clearpage

\fi




\end{document}
